3D Regression Heat Map Analysis of Population Study Data

### 2015-06-24 draft.tex
minor revisions

\paragraph{Regression Analysis Notation.} Regression formulas are usually denoted as follows:
%%
$Dependent \sim Independent_1 + ... + Independent_n$.
% \begin{equation}
% Dependent \sim Independent_1 + ... + Independent_n
% \label{eq:RegressionNotation}
% \end{equation}
%%
An example of a regression formula would be $KidneyDisorder~\sim~Smoking~+~Obesity$.
The most commonly used regression operators comprise:
%%
\begin{itemize}
	\item $+,-$ inclusion/exclusion of the variable (e.g. $x\pm y$),
	\item $:$ inclusion of interactions between the variables (e.g. $x:y$),
	\item $*$ inclusion of the variables as well as their interactions (e.g. $x*y$)
	\item $|$ (conditioning) inclusion of variable x, given y (e.g. $x|y$)
\end{itemize}
%%
The class of the target feature restricts the regression type.
%%
Different regression types are available, we focus on the following:
%%
\paragraph{Linear Regression for Continuous Target.}
%%
The basic type is the linear regression, creating a linear map from the space comprising the \emph{independent} features to the \emph{dependent} features.
%%
The \emph{dependent} variable has to be of \emph{continuous type}.
%%
\add{
%%
Linear regression models can also be described using the \emph{adjusted} $R^2$, which considers the number of dependent features.
%%
It yields lower values, when features with little entropy w.r.t. the target feature are included.
%Additional metrics describing linear regression models comprise of the \emph{adjusted} $R^2$, which also adjusts for the number of dependent features and yields lower values, when features with little entropy towards the target feature are included.
%%
The $f$-$statistic$ determines how much improvement the independent variables will add to the model compared to them being not considered at all.
%%
}

>>>>

\paragraph{Regression Analysis Notation.} Regression formulas are usually denoted as follows:
%%
$Dependent \sim Independent_1 + ... + Independent_n$.
% \begin{equation}
% Dependent \sim Independent_1 + ... + Independent_n
% \label{eq:RegressionNotation}
% \end{equation}
%%
An example of a regression formula would be $KidneyDisorder~\sim~Smoking~+~Obesity$.
The most commonly used regression operators comprise:
%%
\begin{itemize}
	\item $+,-$ inclusion/exclusion of the variable (e.g. $x\pm y$),
	\item $:$ inclusion of interactions between the variables (e.g. $x:y$),
	\item $*$ inclusion of the variables as well as their interactions (e.g. $x*y$)
	\item $|$ (conditioning) inclusion of variable x, given y (e.g. $x|y$)
\end{itemize}
%%
\magenta{
Due to the different meaning of operators in regression formulas, feature transformations are not available within this notation.
}
%%
The class of the target feature restricts the regression type.
%%
Different regression types are available, we focus on the following for describing linear relationships:
%%
\paragraph{Linear Regression for Continuous Target.}
%%
The basic type is the linear regression, creating a linear map from the space comprising the \emph{independent} features to the \emph{dependent} features.
%%
The \emph{dependent} variable has to be of \emph{continuous type}.
%%
\add{
%%
Linear regression models can also be described using the \emph{adjusted} $R^2$, which considers the number of dependent features.
%%
It yields lower values, when features with little entropy w.r.t. the target feature are included.
%Additional metrics describing linear regression models comprise of the \emph{adjusted} $R^2$, which also adjusts for the number of dependent features and yields lower values, when features with little entropy towards the target feature are included.
%%
The $f$-$statistic$ determines how much improvement the independent variables will add to the model compared to them being not considered at all.
%%
}
